Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-03-02 analysis/paper/supplementary-material.Rmd
adjust table and knit the rmd and SI

ft_age_sex <- flextable(age_sex_by_phase) %>% 
  colformat_double(digits = 0) %>%
  set_header_labels(pre_male = "pre-European", pre_female = "pre-European",
                    pre_NA = "pre-European", post_male = "post-European", 
                    post_female ="post-European", post_NA = "post-European") %>%
  merge_at(i = 1, j = 2:4, part = "header") %>% 
  merge_at(i = 1, j = 5:7, part = "header") %>% 
  add_header_row(values = c("","male", "female", "unknown", 
                            "male", "female", "unknown"), top = FALSE) %>% 
  align(j = 2:7, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  set_caption("The number of burials with identification of age and sex at Kiwulan. The NA means no sufficient skeletal remains for determination of age or sex")
ft_age_sex
```

>>>>

ft_age_sex <- flextable(age_sex_by_phase) %>% 
  colformat_double(digits = 0) %>%
  set_header_labels(pre_male = "pre-European", pre_female = "pre-European",
                    pre_NA = "pre-European", post_male = "post-European", 
                    post_female ="post-European", post_NA = "post-European") %>%
  merge_at(i = 1, j = 2:4, part = "header") %>% 
  merge_at(i = 1, j = 5:7, part = "header") %>% 
  add_header_row(values = c("","male", "female", "unknown", 
                            "male", "female", "unknown"), top = FALSE) %>% 
  align(j = 2:7, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  width(j = ~ age, width = 1) %>% 
  width(j = 2:7, width = 0.8) %>% 
  set_caption("The number of burials with identification of age and sex at Kiwulan. The unknown means no sufficient skeletal remains for determination of age or sex")
ft_age_sex
```
